\textcolor[rgb]{0,0,1}{Data-Driven Model Predictive Control using Random Forests for Energy and Thermal Comfort Optimization in Buildings}

### 2018-01-21 paper/final/Response_to_reviewers/Response_to_reviewers.tex

\bigskip

The authors would like to thank the Associate Editor and the Reviewers for their constructive and helpful comments. The following major and minor revisions have been applied (all changes in the manuscript are highlighted in \textcolor[rgb]{0.00,0.00,1.00}{blue colored fonts}):

\begin{itemize}

	\item Section 1 - INTRODUCTION
	\textbf{
	\begin{itemize}
		\item The introduction has been completely re-organized and rewritten in most of its parts, with a more detailed explanation of the paper contribution;
		\item Literature review and related work have been updated;
	\end{itemize}}

	\item Section 2 - COMPLEXITY ISSUES IN MODELING BUILDINGS: PHYSICS-BASED VS DATA-DRIVEN
	\textbf{
	\begin{itemize}
		\item This section has been added to highlight the importance of our contribution, that is data-driven, with respect to model-based approaches;
	\end{itemize}}

	\item Section 3 - DATA PREDICTIVE CONTROL
	\textbf{
	\begin{itemize}
		\item We rewrote the section to make it more clear;
		\item We provided additional details to make the mathematical model description more clear and self-contained;
	\end{itemize}}

	\item Section 6 - CASE STUDY: OPTIMAL HEATING SYSTEM SCHEDULING
	\textbf{
	\begin{itemize}
		\item We highlighted the differences with respect to Section 5;
		\item We added new results that account for weather forecast uncertainties and show the robustness of the proposed approach;
	\end{itemize}}

	\item Minor changes
	\textbf{
	\begin{itemize}
		\item We updated the abstract to make it more complete and clear;
		\item We reviewed the english;
		\item We improved the notation and corrected some mistakes;
	\end{itemize}}

@@

		\item add another section to show how the previous point simplifies using data-driven methods

	\end{itemize}

\item \textbf{Reviewer 1:} \textit{Another point is that in traditional state space model, one cannot measure everything except input and output in most cases. How could we obtain such training data if these data are not measurable.}

\textbf{Authors:} We thank the reviewer for this comment, indeed our previous presentation of the paper was unclear on this fundamental aspect. In our revision we widely illustrate \textbf{in Section 2,} how in traditional state-space models part of the state is measurable (i.e. room temperatures, etc) and part is not measurable (i.e. layers/windows temperatures, etc). In our approach, of course, $(\mathcal{X}^c, \mathcal{X}^d, \mathcal{Y})$ are ALL measurable variables, i.e. variables that are present in the historical data of a building. The unmeasurable variables of the traditional state-space models are not assumed to be measurable in this paper \textbf{and are neglegted in the proposed models}, yet our prediction works well since we compensate \textbf{them} via the regression tree/random forest approaches.

@@

\item \textbf{Reviewer 1:} \textit{The key intuition of the proposed framework is Eq. (1). It would be much better if the authors can explain their framework using Eq. (1) directly first instead of using another set of notations such as $(X^c, X^d, Y)$.}

\textbf{Authors:} We agree with the reviewer. Following this comment, and also other comments, we re-wrote the corresponding Section to make it more clear and complete to describe the DPC technical approach. In particular...

### 2018-01-21 paper/final/main.tex
typo in the title corrected

\title{\textcolor[rgb]{0,0,1}{Data-Driven Model Predictive Control using Random Forests for Energy and Thermal Comfort Optimization in Buildings Energy Systems using Random Forests}}

>>>>

\title{\textcolor[rgb]{0,0,1}{Data-Driven Model Predictive Control using Random Forests for Energy and Thermal Comfort Optimization in Buildings}}
